Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-03 paper/post_tci.tex
First set of changes after Dec-reviews: Std,Custom SSIM, DL Literature, hyperparameter tuning

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  Tomographic reconstruction from undersampled measurements is a
  necessity when the measurement process is potentially harmful, needs
  to be rapid, or is resource-expensive. In such cases, information
  from previously existing longitudinal scans of the same object
  (`object-prior') helps in the reconstruction of the current object
  (`test') from its significantly fewer measurements. A common problem
  with these techniques is the strong influence of object-priors in
  the reconstruction of new regions in the test.  In this work, we
  mitigate this problem by first estimating the location of new
  regions and then imposing object-prior in \textit{only} old regions
  which are similar to the prior.

  Our work is based on longitudinal data acquisition scenarios where
  we wish to study new changes that evolve within an object over time,
  such as in repeated scanning for disease monitoring, or in
  tomography-guided surgical procedures. While reconstruction is easily feasible
  when measurements are acquired from a large number of projection
  angles (`views'), it is challenging when the number of views is
  limited (sub-Nyquist). We show that in the latter case, a
  `spatially-varying' technique is appropriate in order to prevent the
  prior from adversely affecting the reconstruction of new structures
  that are absent in any of the earlier scans. The reconstruction of
  new regions is safeguarded from the bias of the prior by computing
  regional weights that moderate the local influence of the priors. We
  are thus able to effectively reconstruct both the old and the new
  structures in the test. We have tested the efficacy of our method on
  synthetic as well as real projection data, in both 2D and 3D. Our
  method significantly improves the overall quality of reconstructions
  while minimizing the number of measurements needed for imaging in
  longitudinal studies.
\end{abstract}

@@

 With the use of an object-prior, a \emph{new} challenge emerges. The prior
 set $S$ may potentially overwhelm the necessary details, and when
 several prior scans are available, finding the best one is an
 issue. We therefore devise an algorithm that estimates the location
 and magnitude of new changes in the (unknown) test. As we show in
 Section~\ref{sec:method_spatially_varying_prior}, this prevents the prior from adversely affecting the reconstruction of new
 regions in the test. We refer to this method as a
 \textit{spatially-varying} prior-based reconstruction routine, that
 still uses \textit{all} the previous scans in the set $S$, without
 using any of the prior scans \textit{as is}, or endeavoring to choose
 one ``right'' prior. In this way, this work is novel and to be
 contrasted with 
 earlier work. As seen in Fig.~\ref{fig:story} (last column, 20
 views) our method uses the set $S$ to yield a better reconstruction
 than the regularization-only, or the backprojection-only methods.

@@

@@

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
RMSE corresponds to error in intensity values and is a measure of
absolute error. For purposes of normalization, while reporting numbers
we rescale intensity values of both the ground truth and the
reconstructed results to lie between 0 to 1, so that the best possible
RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks to
consider perceptual changes, as well as correlation between adjacent
pixels. This can be useful in a clinical context.  Here, we therefore
assign a higher weightage to structure preservation, that is we assign
the following weights to structure, contrast, and intensity
respectively: $0.7,0.2,0.1$. Our results are optimized for SSIM, but
it can be verified that in all cases for the various datasets
considered, our results are favourable with either metric.

@@

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned in such a way as to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are obviously
not known in advance, and thus not considered for the purpose of
tuning.  Further, this value was retained for our spatially-varying
prior-based reconstruction as well, that is, the value optimized for
the TV-only regularizer is maintained for the method proposed in this
paper.  In principle, one could have jointly optimized both
$\lambda_1$ and $\lambda_2$ to get even better results compared to the
one we have in Sections~\ref{sec:results_with_imaging_model},
and~\ref{sec:results_without_imaging_model}.  The value of $\lambda_2$
largely depends on the amount of artefacts one aims to remove by the
use of object-prior at the cost of their dominance in the new
regions. This value was empirically chosen to lie between $(0,3)$ for
our datasets (having the fixed $\lambda_1$).

@@

    \caption{2D reconstructions for varying values of $k$. The SSIM values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}

@@

Alternatively, in cases where one wishes to completely avoid the use
of this hyper-parameter, one can construct a binary weights-map using
a learning based method described in the supplementary
material~\cite{supp_paper}.

@@

        reconstructed using only $6$ paltry views.  The weights-maps

@@

\caption{SSIM and RMSE of the reconstructions shown in

@@

SSIM & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline

@@

We observe
that our method reconstructs new structures while simultaneously
reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
the reconstructed new regions using various methods. 
%The ground truth and reconstructions are normalized to lie in [0-1].
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
\label{fig:potato_zoomed_2D_results}
\end{figure}
\end{comment}
%-------------------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM (RMSE) within the RoI of reconstructed potato from various
    methods. 
%The SSIM of ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:potato_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.52 (0.36)
& 0.92 (0.06) & \textcolor{red}{0.97 (0.03)} \\ \hline \textbf{3D} & 0.58 (0.26) & 0.75 (0.21) & \textcolor{red}{0.84 (0.16)}
\\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM (RMSE) within the RoI of reconstructed okra from various
    methods. 
%SSIM of the ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The 2D reconstructed images are shown in Fig.~\ref{fig:okra_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.46 (0.28)
& 0.50 (0.24) & \textcolor{red}{0.74 (0.15)} \\ 
\hline \textbf{3D} & 0.65 (0.22) & 0.70 (0.21) & \textcolor{red}{0.71 (0.19)}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
%For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The  reconstructed images are shown in Fig.~\ref{fig:tmh_2D_results},}
\begin{tabular}{|l|c|c|c|c|}
\hline \textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline  0.73 (0.04)
& 0.91 (0.09) & \textcolor{red}{0.95 (0.03)} \\ \hline 
\end{tabular}
\label{table:tmh_ssim}
\end{table}
%-----------------------------------------------------------------

@@

%----------------------------------------------------
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
\label{fig:sprouts_zoomed_2D_results}
\end{figure}
\end{comment}
%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM (RMSE) within the RoI of reconstructed sprouts from various
    methods. 
%The SSIM of ideal reconstruction) is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:sprouts_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
 \\ \hline \textbf{2D} & 0.67 (0.24)
& 0.82 (0.17) & \textcolor{red}{0.86 (0.13)} \\ \hline \textbf{3D} & 0.67 (0.25) & 0.73 (0.23) & \textcolor{red}{0.82 (0.14)}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss computational
complexity of our method and requirements for applying deep learning
techniques in longitudinal few-view reconstruction.
\subsection{Computational Complexity}

@@

\subsubsection{Example Computation}
If the set of projection views for every test is fixed a priori, a
reasonable assumption, the set of low quality reconstructions can be
produced offline and stored in order to save computational costs. 
% Most of the computation time in our technique is used for the
% generation of low quality eigen-space by reconstructing each of the
% templates using TV and FDK. 
With this as the basis, Table~\ref{table:compute_time} shows the
computation times for various stages of reconstruction of a 2D slice
of Liver on MATLAB 2019a on an AMD
2920X 12-Core Processor machine with 64GB RAM. 
% If however, new sets of
% projection views for every test are to be allowed, the low quality
% reconstructions can still be performed efficiently using
% parallelization since these reconstructions are completely
% independent. 
\begin{table}[!h]
 \centering
  \caption{Computation times (in seconds) for various stages of
    reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD
    2920X 12-Core Processor machine with 64GB RAM. Our code is
    available for inspection~\cite{codeRepo}.}
\begin{tabular}{|l|l|l|l|}
\hline
 \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parametric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learned by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.

@@

  Another avenue for using deep networks \textit{within} our current
  work is to replace the currently used fixed eigenspace provided by
  PCA by a learned feature basis provided by a network such as an
  autoencoder. For each dataset, an autoencoder may be trained to
  learn a specific set of latent features. This will again require
  atleast a few tens of volumes. We see this as a future direction of
  work.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  Tomographic reconstruction from undersampled measurements is a
  necessity when the measurement process is potentially harmful, needs
  to be rapid, or is resource-expensive. In such cases, information
  from previously existing longitudinal scans of the same object
  (`object-prior') helps in the reconstruction of the current object
  (`test') from its significantly fewer measurements. A common problem
  with these techniques is the strong influence of object-priors in
  the reconstruction of new changes in the test.  In this work, we
  mitigate this problem by first estimating the location of changes (`new
  regions') and then imposing object-prior in \textit{only} those regions
  which are similar to the prior (`old regions').

  Our work is based on longitudinal data acquisition scenarios where
  we wish to study new changes that evolve within an object over time,
  such as in repeated scanning for disease monitoring, or in
  tomography-guided surgical procedures. While reconstruction is easily feasible
  when measurements are acquired from a large number of projection
  angles (`views'), it is challenging when the number of views is
  limited (sub-Nyquist). We show that in the latter case, a
  `spatially-varying' technique is appropriate in order to prevent the
  prior from adversely affecting the reconstruction of new structures
  that are absent in any of the earlier scans. The reconstruction of
  new regions is safeguarded from the bias of the prior by computing
  regional weights that moderate the local influence of the priors. We
  are thus able to effectively reconstruct both the old and the new
  structures in the test. We have tested the efficacy of our method on
  synthetic as well as real projection data, in both 2D and 3D. Our
  technique significantly improves the overall quality of
  reconstructions while minimizing the number of measurements needed
  for imaging in longitudinal studies. We show that with
  as little as $2\%$ of measurements, our method achieves a structural
  fidelity of $0.84$, with $1.00$ representing ideal reconstruction.
\end{abstract}

@@

 With the use of an object-prior, a \emph{new} challenge emerges. The prior
 set $S$ may potentially overwhelm the necessary details~\cite{mythesis}, and when
 several prior scans are available, finding the best one is an
 issue. We therefore devise an algorithm that estimates the location
 and magnitude of new changes in the (unknown) test. As we show in
 Section~\ref{sec:method_spatially_varying_prior}, this prevents the prior from adversely affecting the reconstruction of new
 regions in the test. We refer to this method as a
 \textit{spatially-varying} prior-based reconstruction routine, that
 still uses \textit{all} the previous scans in the set $S$, without
 using any of the prior scans \textit{as is}, or endeavoring to choose
 one ``right'' prior. In this way, this work is novel and to be
 contrasted with 
 earlier work. As seen in Fig.~\ref{fig:story} (last column, 20
 views) our method uses the set $S$ to yield a better reconstruction
 than the regularization-only, or the backprojection-only methods.

@@

 In the recent past, deep learning based techniques have also been widely used for limited view CT reconstruction without the use of any longitudinal object-prior. For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one obtained from few-view imaging. This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction. Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework. \cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram. \cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction. While all of the above methods predict full-view reconstruction from the measurements of test object alone, we believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use. In this context, we present an analytical method that uses the available longitudinal data to better inform the reconstruction of the test. We first construct a `weights map' that gives clear insights about regions of change within the object over time.

@@

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
RMSE corresponds to error in intensity values and is a measure of
absolute error. For purposes of normalization, while reporting numbers
we rescale intensity values of both the ground truth and the
reconstructed results to lie between 0 to 1, so that the best possible
RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks to
consider perceptual changes, as well as correlation between adjacent
pixels. This can be useful in a clinical context. The SSIM~\cite{multiscale_ssim} also provides a flexibility to set coefficients for the following three factors: Structure, Contrast and Intensity. In all our results, we report SSIM with both the standard setting, i.e., with coefficients $1.0,1.0,1.0$ and a structure-focussed setting, wherein we assign a higher weightage to structure preservation. In the latter case, we assign the following coefficients to the factors Structure, Contrast, and Intensity respectively: $0.7,0.2,0.1$. Our results are optimized for structure-focussed SSIM, but
it can be verified that in all cases for the various datasets
considered, our results are favourable with either metric.

@@

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
The three hyper-parameters, $\lambda_1$, $\lambda_2$ and $k$
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are 
not known in advance, and thus not considered for the purpose of this
tuning. Thus, we compare our reconstruction with the best possible baseline TV reconstruction by choosing the $\lambda_1$ that gives the best SSIM for TV reconstruction. Further, this value was retained for our spatially-varying
prior-based reconstruction as well, that is, the value optimized for
the TV-only regularizer is maintained for the method proposed in this
paper.  In principle, one could have jointly optimized both
$\lambda_1$ and $\lambda_2$ to get even better results compared to the
one we have in Sections~\ref{sec:results_with_imaging_model},
and~\ref{sec:results_without_imaging_model}.

The value of $\lambda_2$
largely depends on the amount of artefacts one aims to remove by the
use of object-prior at the cost of their dominance in the new
regions. This value is chosen omnisciently, i.e., with the chosen $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM. This  was found to lie between $(0,3)$ for
our datasets. In practice however, one may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.

@@

    \caption{2D reconstructions for varying values of $k$. The SSIM (structure-focussed) values for all images are computed within the red RoI (shown in Fig.~\ref{fig:okra_2D_results}(a)), the region where the test is different from all of the previously scanned objects.}

@@

Our supplementary material~\cite{supp_paper} (part-3) discusses an alternate reconstruction method that does not require two of the three hyperparameters: $\lambda_1$ and $\lambda_2$. In this method, the computed weights-map is used to stitch parts of the pilot reconstruction and object-prior based on the weights map, and hence there is no optimization to be solved involving $\lambda_1$ and $\lambda_2$. The computation of weights map alone requires selection of the hyperparameter value k.

@@

        reconstructed using only $6$ views.  The weights-maps

@@

\caption{Standard-SSIM (`SSIM-1'), structure-focussed SSIM (`SSIM-2') and RMSE of the reconstructions shown in

@@

SSIM-1 & 0.31 & 0.48  & 0.39  & 0.51 & 0.55  & 0.42 & 0.68 &\textcolor{red}{0.78} \\ \hline
SSIM-2 & 0.64 & 0.72  & 0.68 & 0.83 & 0.81 & 0.69 & 0.83 &\textcolor{red}{0.88} \\ \hline

@@

We observe
that our method reconstructs new structures while simultaneously
reducing streak artefacts. Table~\ref{table:potato_ssim} shows SSIM and RMSE of
the reconstructed new regions using various methods. 
%The ground truth and reconstructions are normalized to lie in [0-1].
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/6_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_zoomed.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:potato_2D_results}.}
\label{fig:potato_zoomed_2D_results}
\end{figure}
\end{comment}
%-------------------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed potato from various
    methods. 
%The SSIM of ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:potato_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.22, 0.52 (0.36)
& 0.86, 0.92 (0.06) & \textcolor{red}{0.95, 0.97 (0.03)} \\ \hline \textbf{3D} & 0.30, 0.58 (0.26) & 0.56, 0.75 (0.21) & \textcolor{red}{0.72, 0.84 (0.16)}
\\ \hline
\end{tabular}
\label{table:potato_ssim}
\end{table}

@@

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed okra from various
    methods. 
%SSIM of the ideal reconstruction is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The 2D reconstructed images are shown in Fig.~\ref{fig:okra_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline \textbf{2D} & 0.26, 0.46 (0.28)
& 0.27, 0.50 (0.24) & \textcolor{red}{0.56, 0.74 (0.15)} \\ 
\hline \textbf{3D} & 0.52, 0.65 (0.22) & 0.56, 0.70 (0.21) & \textcolor{red}{0.57, 0.71 (0.19)}
\\ \hline
\end{tabular}
\label{table:okra_ssim}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of 2D reconstruction of radio-frequency ablation data of liver from various methods.  
%For ideal reconstruction, SSIM equals 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here.  
The  reconstructed images are shown in Fig.~\ref{fig:tmh_2D_results},}
\begin{tabular}{|l|c|c|c|c|}
\hline \textbf{Backprojection} & \textbf{TV} &
\textbf{This paper} \\ \hline 0.54, 0.73 (0.04)
& 0.80, 0.91 (0.09) & \textcolor{red}{0.90, 0.95 (0.03)} \\ \hline 
\end{tabular}
\label{table:tmh_ssim}
\end{table}
%-----------------------------------------------------------------

@@

%----------------------------------------------------
\begin{comment}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/test_zoomed.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp_zoomed.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_zoomed.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_pca_zoomed.png}}
\caption{A zoomed-in version of the regions around the RoI of the reconstructions shown in Fig.~\ref{fig:sprouts_2D_results}}
\label{fig:sprouts_zoomed_2D_results}
\end{figure}
\end{comment}
%--------------------------------------------------------------
\begin{table}[!h]
  \centering
  \caption{Standard-SSIM, structure-focussed SSIM (RMSE) within the RoI of reconstructed sprouts from various
    methods. 
%The SSIM of ideal reconstruction) is 1. The ideal RMSE is 0, and the worst RMSE possible is 1 here. 
The 2D reconstructed images are shown in Fig.~\ref{fig:sprouts_2D_results}, and 3D reconstructed volumes can be seen in~\cite{supp_paper}.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline &
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
 \\ \hline \textbf{2D} & 0.42, 0.67 (0.24)
& 0.61, 0.82 (0.17) & \textcolor{red}{0.72, 0.86 (0.13)} \\ \hline \textbf{3D} & 0.44, 0.67 (0.25) & 0.47, 0.73 (0.23) & \textcolor{red}{0.66, 0.82 (0.14)}
\\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}

@@

\section{Computational Complexity}
\label{sec:discussion}
%In this section, we discuss computational
%complexity of our method and requirements for applying deep learning
%techniques in longitudinal few-view reconstruction.
%\subsection{Computational Complexity}

@@

\subsubsection{Example Computation}
If the set of projection views for every test is fixed a priori, a
reasonable assumption, the set of low quality reconstructions can be
produced offline and stored in order to save computational costs. 
% Most of the computation time in our technique is used for the
% generation of low quality eigen-space by reconstructing each of the
% templates using TV and FDK. 
With this as the basis, Table~\ref{table:compute_time} shows the
computation times for various stages of reconstruction of a 2D slice
of Liver on MATLAB 2019a on an AMD
2920X 12-Core Processor machine with 64GB RAM. 
% If however, new sets of
% projection views for every test are to be allowed, the low quality
% reconstructions can still be performed efficiently using
% parallelization since these reconstructions are completely
% independent. 
\begin{table}[!h]
 \centering
  \caption{Computation times (in seconds) for various stages of
    reconstruction of a (512$\times$512) 2D slice of Liver from 30 views, on MATLAB 2019a on an  AMD
    2920X 12-Core Processor machine with 64GB RAM. Our code is
    available for inspection~\cite{codeRepo}.}
\begin{tabular}{|l|l|l|l|}
\hline
 \begin{tabular}[c]{@{}l@{}} FBP \end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\begin{comment}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parametric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learned by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.

@@

  Another avenue for using deep networks \textit{within} our current
  work is to replace the currently used fixed eigenspace provided by
  PCA by a learned feature basis provided by a network such as an
  autoencoder. For each dataset, an autoencoder may be trained to
  learn a specific set of latent features. This will again require
  atleast a few tens of volumes. We see this as a future direction of
  work.
\end{comment}
